Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-29 prop_iop.tex
prop_iop.tex \subsection{Quantum {\normalsize{}$\mathscr{I}_{\mathrm{D}}$}-valued Probability Measures} Updating...

\begin{proof}Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures called $\mu:\events\rightarrow\left\{ 1,0\right\} $.
By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.
Since $\mu$ is a probability measure, there is only one pair of $\left(s_{0},i_{0}\right)$
such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$. Therefore, 
\[
\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}
\]
\end{proof}

\begin{thm}\label{cor:Kochen-Specker-expectation}Given a Hilbert
space of dimension~$d\ge3$, there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
where $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
as before.\end{thm}

\begin{proof}\end{proof}

>>>>

\begin{proof}Adopt the definitions in subsection~\ref{subsec:Between-Expectation-Values-Classical-Quantum}.
By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$ are the same
real-valued probability measures, and is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
By lemma~\ref{lemma:expectation-singleton}, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one pair
of $\left(s_{0},i_{0}\right)$ such that $\mu\left(P_{i_{0}}^{s_{0}}\right)=1$.
Therefore, 
\begin{equation}
\expval{\mathbf{O}}_{\rho}\stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)=\lambda_{i_{0}}^{s_{0}}\textrm{ .}\label{eq:expectation-value-eigenvalue}
\end{equation}
\end{proof}

Given two singleton sets~$\left\{ \lambda_{1}\right\} $ and $\left\{ \lambda_{2}\right\} $,
it is intuitive to define their multiplication of to be $\left\{ \lambda_{1}\lambda_{2}\right\} $
which gives the following lemma.

\begin{lemma}For any sequence of commuting observables~$\left\{ \mathbf{O}_{j}\right\} $,
\begin{equation}
\prod_{j}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j}\mathbf{O}_{j}}_{\bar{\mu}}\textrm{ .}\label{eq:Kochen-Specker-Rules}
\end{equation}
\end{lemma}

\begin{proof}Since $\left\{ \mathbf{O}_{j}\right\} $ is a sequence
of commuting observables, they can be diagonalized by a common orthonormal
basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$. By lemma~\ref{lemma:QIVPM2QCM},
$\mul$ and $\mur$ are the same cryptodeterministic measure, and
is simply denoted by $\mu:\events\rightarrow\left\{ 1,0\right\} $.
Since $\mu$ is a cryptodeterministic measure, there is only one $j_{0}$
such that $\mu\left(\proj{j_{0}}\right)=1$. Therefore, by the same
reason as equation~(\ref{eq:expectation-value-eigenvalue}), the
both sides of equation~(\ref{eq:Kochen-Specker-Rules}) are the product
of eigenvalues corresponding to eigenstate~$\ket{j_{0}}$, and should
be equal.\end{proof}

Based on the previous lemmas, we could follow Mermin's idea to prove
the Kochen-Specker theorem again~\cite{Mermin1990Simple,peres1995quantum}.

\begin{thm}\label{thm:Kochen-Specker-expectation}Given a Hilbert
space of dimension~$d\ge3$, there is no quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
where $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $
as before.\end{thm}

\begin{proof}Since the expectation value~$\expval{\cdot}_{\bar{\mu}}$
satisfying the previous lemmas, the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a IVPM~$\bar{\mu}$ such
that 
\begin{equation}
\begin{array}{ccc}
\expval{\mathbb{1}\otimes\sigma_{z}}_{\bar{\mu}} & \expval{\sigma_{z}\otimes\mathbb{1}}_{\bar{\mu}} & \expval{\sigma_{z}\otimes\sigma_{z}}_{\bar{\mu}}\\
\expval{\sigma_{x}\otimes\mathbb{1}}_{\bar{\mu}} & \expval{\mathbb{1}\otimes\sigma_{x}}_{\bar{\mu}} & \expval{\sigma_{x}\otimes\sigma_{x}}_{\bar{\mu}}\\
\expval{\sigma_{x}\otimes\sigma_{z}}_{\bar{\mu}} & \expval{\sigma_{z}\otimes\sigma_{x}}_{\bar{\mu}} & \expval{\sigma_{y}\otimes\sigma_{y}}_{\bar{\mu}}
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).\end{proof}
